\documentclass[aspectratio=169]{beamer}
\usetheme{Madrid}

\title[Objectives]{BRIDGES Summer Workshop:\\Objectives}
\subtitle{}
\author{Kalpathi Subramanian, Erik Saule\\\texttt{krs@uncc.edu}, \texttt{esaule@uncc.edu}}
\institute{The University of North Carolina at Charlotte}
\date{BRIDGES Summer Workshop 2022}

\setbeamertemplate{footline}

\usepackage{hyperref,graphicx}
\usepackage{subfloat}

\beamertemplatenavigationsymbolsempty % remove navigation symbols
\begin{document}


\begin{frame}
\titlepage

\end{frame}


\begin{frame}
  \frametitle{Introductions}

  \begin{itemize}
  \item Who we are
  \item Who you are
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Goals and Objectives}

  \begin{columns}
    \column{.44\linewidth}
    \begin{block}{Course Structure}
      \begin{itemize}
      \item How should I structure my course?
      \item What should I cover in my course?
      \item What are other people doing?
      \end{itemize}
    \end{block}

    \column{.53\linewidth}
    \begin{block}{Course Content}
      \begin{itemize}
      \item How to foster students interest?
      \item How to make your course appear relevant?
      \item How to make your course fun?
      \end{itemize}
    \end{block}

   BRIDGES will help with that.
  \end{columns}

  \begin{block}{By the end of the workshop}
    \begin{itemize}
    \item You will have a better understanding of the structure of your class.
    \item You will have an understanding of BRIDGES.
    \item You will be ready to deploy 3 BRIDGES activities in your course next semester.
    \end{itemize}
  \end{block}
\end{frame}


\begin{frame}
  \frametitle{Organization}

  Day 1:
  \begin{itemize}
  \item Introductions
  \item Objectives
  \item Understanding the structure of your course and opportunities
  \item Learning BRIDGES practically
  \end{itemize}
  
  Day 2:
  \begin{itemize}
  \item Planning which interventions to do
  \item Designing the first intervention
  \item Designing the second intervention
  \end{itemize}

  
  Day 3:
  \begin{itemize}
  \item Designing third  interventions
  \item Reflecting
  \item Planning for next semester
  \end{itemize}
  
\end{frame}


\end{document}
%
