\hypertarget{index_overview_sec}{}\section{Overview}\label{index_overview_sec}
The Bridging Real-\/world Infrastructure Designed to Goal-\/align, Engage, and Stimulate (B\+R\+I\+D\+G\+E\+S) project is directed at improving the retention of sophomore students in Computer Science by (1) introducing real-\/world datasets (Facebook, Twitter, etc) into course projects involving computer science data structures, and (2) facilitating peer mentoring of sophomores by senior C\+S students in shared lab experiences that involve the use of the B\+R\+I\+D\+G\+E\+S infrastructure in software development. \hypertarget{index_br_client}{}\section{B\+R\+I\+D\+G\+E\+S Client Design}\label{index_br_client}
B\+R\+I\+D\+G\+E\+S client side design loosely follows the basic data structure elements implemented and described in ``\+A Practical Introduction to Data Structures and Algorithm Analysis" by C.\+A. Shaffer (\href{http://people.cs.vt.edu/shaffer/Book/}{\tt http\+://people.\+cs.\+vt.\+edu/shaffer/\+Book/}). These elements are augmented to contain visual properties that are controlled by the user to customize the visual representation of the constructed data structure. Once a a data structure is ready to be visualized, related B\+R\+I\+D\+G\+E\+S server calls are made to send a reprsentation of the data structure to B\+R\+I\+D\+G\+E\+S server. \hypertarget{index_br_server}{}\section{B\+R\+I\+D\+G\+E\+S Server Design.}\label{index_br_server}
B\+R\+I\+D\+G\+E\+S server implements a combination of technologies (Mongo\+D\+B, Node, d3\+J\+S(visualization) to receive a data structure representation for visualization. These are largely transparent to the user and involves the user being directed to a web page for viewing the data structure. Attention has been paid to provide meaningful error messages to the user in case problems are encountered in the process. \hypertarget{index_api_sec}{}\section{A\+P\+I Descriptions.}\label{index_api_sec}
See the accompanying pages for detailed description of the B\+R\+I\+D\+G\+E\+S classes \hypertarget{index_sponsor_sec}{}\subsection{Sponsorship/\+Funding.}\label{index_sponsor_sec}
B\+R\+I\+D\+G\+E\+S is an N\+S\+F T\+U\+E\+S Project.\hypertarget{index_contacts_sec}{}\section{Contacts\+:}\label{index_contacts_sec}
Kalpathi Subramanian, \href{mailto:krs@uncc.edu}{\tt krs@uncc.\+edu}, Jamie Payton, \href{mailto:payton@temple.edu}{\tt payton@temple.\+edu}, Erik Saule, \href{mailto:esaule@uncc.edu}{\tt esaule@uncc.\+edu}

Department of Computer Science, The University of North Carolina at Charlotte, Charlotte, N\+C. 