\documentclass[aspectratio=169]{beamer}
\usetheme{Madrid}

\title[Objectives]{BRIDGES Summer Workshop:\\Objectives}
\subtitle{}
\author{Kalpathi Subramanian$^1$, Erik Saule$^1$, Jamie Payton$^2$, and Matthew Mcquaigue$^1$ \\\texttt{krs@uncc.edu}, \texttt{esaule@uncc.edu}, \texttt{payton@temple.edu}, \texttt{mmcquaig@uncc.edu}}
\institute{$^1$The University of North Carolina at Charlotte\\$^2$Temple University}
\date{BRIDGES Summer Workshop 2022}

\setbeamertemplate{footline}

\usepackage{hyperref,graphicx}
\usepackage{subfloat}

\beamertemplatenavigationsymbolsempty % remove navigation symbols
\begin{document}


\begin{frame}
\titlepage

\end{frame}


\begin{frame}
  \frametitle{Introductions}

  \begin{itemize}
  \item Who we are
  \item Who you are
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Goals and Objectives}

  \begin{columns}
    \column{.49\linewidth}
    \begin{block}{Course Structure}
      \begin{itemize}
      \item How should I structure my course?
      \item What shoud I cover in my course?
      \item What are other people doing?
      \end{itemize}
    \end{block}
    
    \column{.49\linewidth}
    \begin{block}{Course Content}
      \begin{itemize}
      \item How to foster students interest?
      \item How to make your course appear relevant?
      \item How to make your course look fun?
      \end{itemize}
    \end{block}
    
  \end{columns}

  We will talk about how curriculum guidelines can help us with
  building better courses.
  
  We will talk about how to drive student engagement.
  
  We will present two tools to help with those.
  \begin{itemize}
  \item CS Materials
  \item BRIDGES
  \end{itemize}
\end{frame}



\begin{frame}
  \frametitle{Organization}

  Day 1:
  \begin{itemize}
  \item introductions
  \item objectives
  \item Understanding the structure of your course and opportunities
  \end{itemize}
  
  Day 2:
  \begin{itemize}
  \item Learning BRIDGES practically
  \item Planning which interventions to do
  \item Designing the first intervention
  \end{itemize}

  
  Day 3:
  \begin{itemize}
  \item Designing 2 more interventions
  \item Reflecting
  \item Planning for next semester
  \end{itemize}
  
\end{frame}


\end{document}
%
